
% \title{Resume}
% \author{Cindy Liu}
% \date{August 2022}



\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{xcolor}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% experience
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt} % original -7
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}


% projects
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Cindy Liu} \\ \vspace{1pt}
    \small +1 647-639-5158 \hspace{1pt} $|$ \hspace{1pt}
    {\faIcon{envelope}}
    \href{mailto:xian.liu@alum.utoronto.ca}{\underline{xian.liu@alum.utoronto.ca}} \hspace{1pt} $|$ \hspace{1pt}   
    \textcolor{blue}{\faIcon{linkedin}}
    \href{https://www.linkedin.com/in/cinnyb2/}
    {\underline{cinnyb2}} \hspace{1pt} $|$ \hspace{1pt}
    \textcolor{orange}{\faIcon{github}}
    \href{https://github.com/cinnyb2/}
    {\underline{cinnyb2}}
    
     
\end{center}


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, SQL, Ruby, JavaScript, TypeScript, Java, C/C++ } \\
     \textbf{Frameworks and Databases}{: Ruby on Rails, Vue.js, React, Node.js, Jest.js, Knex.js, MySQL, PostgresSQL} \\
     \textbf{Tools}{: Git, Docker, AWS, Kubernetes, Jira, TestRail, DataDog, CI/CD, LaTeX} \\
  
\end{itemize}


%-----------EXPERIENCE-----------

\section{Experience}

\resumeSubHeadingListStart
\resumeSubheading
    {Software Developer Intern}{Aug. 2022 -- Dec. 2022}
    {Vidyard}{Remote}
  \resumeSubheading
    {Software Developer Intern}{May. 2022 -- Aug. 2022}
    {Vidyard}{Remote}
         \resumeItemListStart
          \resumeItem{Implemented key scripts to address Youtube API security vulnerabilities within the platform and automate the process of recording analytic to monitor future vulnerabilities \emph{(Node.js, TypeScript, Knex.js, Objection.js MySQL, DataDog)}}
           \resumeItem{Lead mini project as sole developer with product manager and UX designer to revamp the front-end administrative flow of the user's page and fix critical bugs, reducing the number of support calls regarding project\% \emph{(Vue.js, JavaScript, Jest.js)}}
            \resumeItem{Manage data migrations and implemented new endpoints in the database for tables with $>$ 2 million columns \emph{(Rails, Jest.js)}}
            \resumeItem{Actively Refactoring legacy code and replacing the contents with clean scalable code that has high unit test coverage and is easily maintained}
           \resumeItemListEnd
\resumeSubheading
    {Junior Full Stack Developer}{Jan. 2022 -- April 2022}
    {Calico Logic}{Vancouver, BC}
        \resumeItemListStart
          \resumeItem{Integrated core automated PDF generator feature that pipeline user data from the database and generate a personalized report, increasing efficiency by 80\% and reducing the number of staff needed by 50\% \emph{(Vue.js, FastAPI, WeasyPrint, Python, PostgreSQL)}}
          \resumeItem{Coordinated with head software engineer to identify the features that needs to be implemented according to the client's requirements and completed the MVP product in 6 months}
            \resumeItem{Designed and implemented two new API endpoints for two separate user flow}
          \resumeItem{Improved mobile user experience by adapting a mobile first design methodology and transforming the web application to be responsive on all devices \emph{(React, $\#C$, ASP.NET CORE, Swagger)}}
        \resumeItemListEnd
       
\resumeSubheading
    {Application Analyst Intern}{Aug. 2021 -- Dec. 2021}
    {Serco Inc.}{Remote}
    \resumeItemListStart
       \resumeItem{Analyzed and summarized Google Analytics into easy to understand interactive data visualizations and create\\ UML diagrams to explain business needs and use cases \emph{(Microsoft SQL Sever, Google Analytics, Lucidchart, Excel)}}
        \resumeItem{Implemented bug fixes and stylistic improvements with the web development team on a website with more than 10,000 daily users \emph{(Angular, CSS, HTML)}}
      \resumeItemListEnd
      
    \resumeSubheading
    {Software QA Intern}{May 2021 -- Aug. 2021}
    {Serco Inc.}{Remote}
    \resumeItemListStart
       \resumeItem{Planned, coordinated and implemented both manual and automated testing projects in a timely manner to ensure that applications are within system requirements \emph{(Jira, TestRail)}}
        \resumeItem{Worked collaboratively with QA, IT, development, and business groups to complete comprehensive testing \\ on 5 major new releases, one of which reduced bandwidth and improved user's login wait time by 30 minutes}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}

    \resumeSubHeadingListStart 
    \resumeProjectHeading
           {\href{https://github.com/cinnyb2/Toliet-Buddy}{\textbf{Toilet Buddy}} $|$\emph{ Python, Fast API, Univorn, Google Maps API, Twilio API, Javascript, Firebase, Figma}}
          {Mar. 2022}
          \resumeItemListStart
                      \resumeItem{{Web application allows you to find the nearest public washroom in SF and notifies your phone when you are near a washroom \textbf{Awarded Best Data Science Hack}}}
          \resumeItemListEnd
          
    \resumeProjectHeading
           {\href{https://devpost.com/software/senior-connect-loam6n}{\textbf{LinkAge}} $|$ \emph{Twilio API, HTML, CSS, Javascript, Firebase, Bootstrap, Figma, Git}}
          {Mar. 2022}
          \resumeItemListStart
                      \resumeItem{{Web application created to alleviate loneliness in the elderly by connecting them to vetted volunteers through video and text chats, \textbf{winners of Telus, Hootsuite,} and \textbf{Twilio challenges}}}
          \resumeItemListEnd

                    \resumeProjectHeading
          {\href{https://devpost.com/software/smart-stove}{\textbf{Smart Stove}} $|$ \emph{C ++, JavaScript, Git, Node-RED, Arduino, Adobe XD}}{Mar. 2020}
          \resumeItemListStart
            \resumeItem{Developed product that monitors the temperature, gas level, and humidity, was \textbf{awarded Best Hardware Hack}}
            \resumeItem{Implemented continuous delivery of real-time data to user's mobile or desktop device with graphs and meter visualization}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

    
  %-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Toronto, Trinity College}{Toronto, ON}
      {Honours Bachelor of Science in Neuroscience and Ecology \& Evolutionary Biology}{Sept. 2016 -- Jun. 2021}
      
%       \smallskip \smallskip
      
%       {Courses: Intro Python, Human Computer Interaction, Statistics for Data Science, History of Artificial Intelligence, and Computers \& Society}
     \resumeSubheading
      {British Columbia Institute of Technology} {Vancouver, BC}
      {Diploma in Computer Systems Technology}{Sept. 2021 -- Mar. 2022}
 
  \resumeSubHeadingListEnd

\end{document}